### 2017-09-29 TF-vldb2018/sec-intro.tex

Incremental algorithms (see \cite{inc-survey,FanHT17} for a survey) have proven usefulness in a variety of applications,
and have been studied for graph pattern matching~\cite{FanLMTWW10,FanWW13-tods} and team formation \cite{ArisLuca12} as well.
However, \cite{inc-survey,FanHT17,FanLMTWW10,FanWW13-tods} only consider data updates,
and \cite{ArisLuca12} only consider continuous coming new tasks. In this work, we  deal with both pattern and data updates for team formation, and support both insertions and deletions. To our knowledge, this is the first study on pattern updates, and is the most general and practical dynamic setting considered so far.

>>>>

Incremental algorithms (see \cite{inc-survey,FanHT17} for a survey) have proven usefulness in a variety of applications,
and have been studied for graph pattern matching~\cite{FanLMTWW10,FanWW13-tods} and team formation \cite{ArisLuca12} as well.
However, \cite{inc-survey,FanHT17,FanLMTWW10,FanWW13-tods} only consider data updates,
and \cite{ArisLuca12} only considers continuous coming new tasks. In this work, we  deal with both pattern and data updates for team formation, and support both insertions and deletions. To our knowledge, this is the first study on pattern updates, and is the most general and practical dynamic setting considered so far.
